Neighborhoods and Felony Disenfranchisement: The Case of New York City

### 2019-06-19 markdown/felony_disenfranchisement_nys.Rmd
rename

---
title: "Neighborhoods and Felony Disenfranchisement: The Case of New York City"
author: "Kevin Morris"
date: "`r format(Sys.time(), '%B %d, %Y')`"
output:
  bookdown::pdf_document2:
    toc: yes
    fig_caption: yes
    latex_engine: xelatex
bibliography: "../research/citations.bib"
biblio-style: chicago
link-citations: yes
fontsize: 12pt
header-includes:
    - \usepackage{setspace}\doublespacing
---
<!-- --- -->
<!-- title: "Neighborhoods and Felony Disenfranchisement: The Case of New York City" -->
<!-- author: "Kevin Morris" -->
<!-- date: "`r format(Sys.time(), '%B %d, %Y')`" -->
<!-- output: word_document -->
<!-- bibliography: "../research/citations.bib" -->
<!-- link-citations: yes -->
<!-- always_allow_html: yes -->
<!-- --- -->

```{r setup, echo = F, message = F, warning = F}
knitr::opts_knit$set(root.dir = "..", dev = "cairo_pdf")
library(systemfit)
library(AER)
library(sandwich)
library(lmtest)
library(scales)
library(tidyverse)
library(extrafont)
library(kableExtra)
library(stargazer)
loadfonts()
```
\pagenumbering{gobble}
\pagenumbering{gobble}
\newpage
\pagenumbering{arabic}
# Introduction {-}

@@

@@

Adding controls for time in Table \ref{tab:to-18-logit-short} increases the AIC, indicating that the inclusion of these variables is not warranted. A Chi-squared test confirms that the model is not improved when controls for time are included.^[[Appendix C] provides further corroboration that being discharged from parole in the months before an election is uncorrelated with propensity to vote by exploring turnout rates in the 2016 presidential election.]

Because the date of parole discharge is not correlated with turnout, we can conceptualize the timing of Executive Order 181 as a randomly assigned treatment variable. An individual who was released after the EO was signed is part of the intend-to-treat group, and individuals who actually had their rights restored comply with the treatment. As with true randomized control trials, compliance (restoration) is correlated with the outcome of interest (turnout) and therefore must be controlled for.

>>>>

---
title: "Neighborhoods and Felony Disenfranchisement: The Case of New York City"
author: "Kevin Morris"
date: "`r format(Sys.time(), '%B %d, %Y')`"
output:
  bookdown::pdf_document2:
    toc: no
    fig_caption: yes
    latex_engine: xelatex
bibliography: "../research/citations.bib"
biblio-style: apalike
link-citations: yes
header-includes:
    - \usepackage{setspace}\doublespacing
---
<!-- --- -->
<!-- title: "Neighborhoods and Felony Disenfranchisement: The Case of New York City" -->
<!-- author: "Kevin Morris" -->
<!-- date: "`r format(Sys.time(), '%B %d, %Y')`" -->
<!-- output: word_document -->
<!-- bibliography: "../research/citations.bib" -->
<!-- link-citations: yes -->
<!-- always_allow_html: yes -->
<!-- --- -->
\pagenumbering{gobble}
\tableofcontents
\pagebreak
```{r setup, echo = F, message = F, warning = F}
knitr::opts_knit$set(root.dir = "..", dev = "cairo_pdf")
library(systemfit)
library(AER)
library(sandwich)
library(lmtest)
library(scales)
library(tidyverse)
library(extrafont)
library(kableExtra)
library(stargazer)
loadfonts()
```
\pagenumbering{arabic}
# Introduction {-}

@@

\pagebreak

@@

The inclusion of time controls in Table \ref{tab:to-18-logit-short} increases the AIC. A Chi-squared test confirms that the model is not improved when controls for time are included.^[[Appendix C] provides further corroboration that being discharged from parole in the months before an election is uncorrelated with propensity to vote by exploring turnout rates in the 2016 presidential election.] Over the short term, the length of time an individual has been off parole is not associated with his propensity to vote.

Because the date of parole discharge is not correlated with turnout, we can conceptualize the timing of Executive Order 181 as a randomly assigned treatment. An individual who was released after the Executive Order went into effect is part of the intend-to-treat group, and individuals who actually had their rights restored "comply" with the treatment. As with many true randomized control trials, compliance (restoration) is correlated with the outcome of interest (turnout) and therefore must be controlled for.
